Visualizations for the manuscript

### 2022-10-04 metanalysis_visualization/manuscript_Figures.Rmd
axis labels formatted for publication

```{r}
bootstrapped_fitted_all %>%
  mutate( time_p = as.Date(time_p)+ 15,
          time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p))%>%
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE), ncol = 2) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all %>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ] 
            %>% mutate(time_p = as.Date(time_p)+ 15, 
                       time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all %>% mutate( time_p = as.Date(time_p)+ 15),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom")

@@

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate( time_p = as.Date(time_p)+ 15,
          time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p))%>%
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ] %>% 
              mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ]%>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",]  
             %>% mutate( time_p = as.Date(time_p)+ 15),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  #scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 10),
         panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

@@

```{r bootstrap_plot, include=FALSE}
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.005) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  #geom_label(data = plot_annotations_sex_df,
  #           aes(label = label),
  #           x = -Inf,
  #           y = +Inf,
  #           hjust = 0,
  #           vjust = 1,
  #           size = 4,
  #           inherit.aes = FALSE) +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.69,
           #label = "Female proportion", 
           label = "Female proportion [Coefficient difference: 0.77 (pvalue: <0.01)]", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.3,
           #label = "Male proportion", 
           label = "Male proportion [Coefficient difference: -0.77 (pvalue: 0.005)]", 
           fill = "#B2DF8A") +
  # annotate("text", x = 7, y = 0.15, label = "Male proportion") +
  labs(
    #title = "Patients sex proportion trends among psychiatric-related visits",
    #   subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"))

@@

```{r}
bootstrapped_fitted_disorder %>% 
  mutate( time_p = as.Date(time_p)+ 15,
          time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p))%>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_disorder %>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_disorder[quantile_bootstrapped_fitted_disorder$quantiles == "50%", ] %>%
              mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = period)) +
  geom_point(data = filter(perc_disorder_group_total  %>% mutate( time_p = as.Date(time_p)+ 15),
                           disorder_group %in% disorders_to_select),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    # subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom") 
ggsave("figure3_boostrapped_disorders.png", height = 15, width = 25, units = "cm")

@@

```{r}
perc_disorder_group_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

@@

counts_plot <- counts2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  facet_wrap2("plotsLabel", axes = "all", scales ="free", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 10), 
        axis.text.y=element_text( size = 10),
        axis.title.y = element_text( size = 9),
        strip.text = element_text(size = 11, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_plot
ggsave("figure_supp1A_counts_per_site.png",counts_plot, height = 25, width = 40, units = "cm")

@@

counts_agg2plot <- counts_agg2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 10), 
        axis.text.y=element_text( size = 10),
        axis.title.y = element_text( size = 9),
        strip.text = element_text(size = 11, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_agg2plot
ggsave("figure_supp1B_counts_all.png",counts_agg2plot, height = 20, width = 32, units = "cm")

>>>>

```{r}
bootstrapped_fitted_all %>%
  mutate( time_p = as.Date(time_p)+ 15,
          time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p))%>%
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE), ncol = 2) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all %>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ] 
            %>% mutate(time_p = as.Date(time_p)+ 15, 
                       time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all %>% mutate( time_p = as.Date(time_p)+ 15),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom")

@@

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate( time_p = as.Date(time_p)+ 15,
          time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p))%>%
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ] %>% 
              mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ]%>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",]  
             %>% mutate( time_p = as.Date(time_p)+ 15),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  #scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 10),
         panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

@@

```{r bootstrap_plot, include=FALSE}
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.005) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  #geom_label(data = plot_annotations_sex_df,
  #           aes(label = label),
  #           x = -Inf,
  #           y = +Inf,
  #           hjust = 0,
  #           vjust = 1,
  #           size = 4,
  #           inherit.aes = FALSE) +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.69,
           #label = "Female proportion", 
           label = "Female proportion [Coefficient difference: 0.77 (pvalue: <0.01)]", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.3,
           #label = "Male proportion", 
           label = "Male proportion [Coefficient difference: -0.77 (pvalue: 0.005)]", 
           fill = "#B2DF8A") +
  # annotate("text", x = 7, y = 0.15, label = "Male proportion") +
  labs(
    #title = "Patients sex proportion trends among psychiatric-related visits",
    #   subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"))

@@

```{r}
bootstrapped_fitted_disorder %>% 
  mutate( time_p = as.Date(time_p)+ 15,
          time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p))%>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("disorder_group",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_disorder %>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_disorder[quantile_bootstrapped_fitted_disorder$quantiles == "50%", ] %>%
              mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
                  time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
                  time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
                  time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
                  time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
                  time_p = as.Date(time_p)),
            aes(y = value, group = period)) +
  geom_point(data = filter(perc_disorder_group_total  %>% mutate( time_p = as.Date(time_p)+ 15),
                           disorder_group %in% disorders_to_select),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_disorder_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    # subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom") 
ggsave("figure3_boostrapped_disorders.png", height = 15, width = 25, units = "cm")

@@

```{r}
perc_disorder_group_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

@@

counts_plot <- counts2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  facet_wrap2("plotsLabel", axes = "all", scales ="free", labeller = label_wrap_gen(width = 35,multi_line = TRUE)) + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 10), 
        axis.text.y=element_text( size = 10),
        axis.title.y = element_text( size = 9),
        strip.text = element_text(size = 11, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_plot
ggsave("figure_supp1A_counts_per_site.png",counts_plot, height = 25, width = 40, units = "cm")

@@

counts_agg2plot <- counts_agg2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 10), 
        axis.text.y=element_text( size = 10),
        axis.title.y = element_text( size = 9),
        strip.text = element_text(size = 11, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
counts_agg2plot
ggsave("figure_supp1B_counts_all.png",counts_agg2plot, height = 20, width = 32, units = "cm")
